% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Daniel Carmody}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%\def\footerlink{www.com/link}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {physics, plasma, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://www.wisc.edu/}{University of Wisconsin - Madison} \\
  Physics Department \\
  1150 University Avenue \\
  Madison, WI 53706
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: &  (412) 596-5355\\
    Email: & \href{mailto:dcarmody@wisc.edu}{\tt dcarmody@wisc.edu} \\
    Homepage: & \href{http://www.danielcarmody.net/}{\tt http://www.danielcarmody.net/} \\
  \end{tabular}
\end{minipage}


%\section*{Personal}


\section*{Education}

\begin{itemize}
	\item PhD (In Progress), Physics, University of Wisconsin - Madison, (September 2009 - current).
\begin{itemize}
\item Investigating the characteristics of microinstabilities and the nature of turbulence and transport in fusion plasmas, with attention to the reversed field pinch device. A mixture of analytic and computational methods are used, the latter of which involve massively parallel simulations on advanced HPC systems. Thesis Advisor: Paul Terry.
\end{itemize}
	\item Master of Advanced Study (Part III of the
 Mathematical Tripos), Department of Applied Mathematics and Theoretical Physics, University of Cambridge, 2009.
 \begin{itemize}
	\item Thesis: 'Constraining Cosmological Inflation'. Thesis Advisor: Paul Shellard.
\end{itemize}
	\item Bachelor of Science, Physics, Carnegie Mellon University, 2008.

\end{itemize}

%\section*{Research Experience}
\section*{Experience}

\begin{itemize}
\item Research Assistant, Theoretical Plasma Physics, University of Wisconsin, 2010-present.
\item Teaching Assistant, Introductory Physics, University of Wisconsin, 2009-2010
\item Physics Tutor, Carnegie Mellon University, 2006-2008.
\item Research Experience for Undergraduates, Cornell University, Summer 2007
\begin{itemize}
\item Modeled electron cloud physics in the Cornell Electron Storage Ring (CESR) with the ECLOUD program. This work was completed to help provide part of the basis for a proposed conversion of CESR to operation as a test accelerator.
\end{itemize}
\item Research Experience for Undergraduates, University of Minnesota, Summer 2006
\begin{itemize}
\item Used seismic data and inverse modeling to map the structure and composition of the earth's mantle beneath the South American continent.
\end{itemize}
\item Intern, Science Applications International Corporation, Summer 2004
\begin{itemize}
\item Updated a GUI in Microsoft's Visual Studio.
\end{itemize}
\end{itemize}


\section*{Honors, Awards, and Fellowships}

\begin{itemize}
\item Cambridge Overseas Trust Scholar, 2008
\item Phi Kappa Phi Honor Society, 2008
\item Phi Beta Kappa Honor Society, 2008
\end{itemize}

\section*{Publications}

\subsection*{Journal Articles}

\begin{itemize}
\item {\bf D.~Carmody}, M.~J. Pueschel, P.~W. Terry, {\it Microturbulence Studies of Pulsed Poloidal Current Drive Discharges in the Reversed Field Pinch}, {\bf submitted to Phys. Plasmas}
\item {\bf D.~Carmody}, P.~W. Terry, M.~J. Pueschel, {\it Gyrokinetic Studies of Microinstabilities in the Reversed Field Pinch}, Phys. Plasmas {\bf 20}, 052110 (2013)
\item P.~W. Terry, M.~J. Pueschel, {\bf D. Carmody}, W.~M.~Nevins, {\it The Effect of Magnetic Flutter on Residual Flow}, Phys. Plasmas {\bf 20}, 112502 (2013)
\end{itemize}

\subsection*{Abstracts and Poster Presentations}

\begin{itemize}
\item Talk, {\it Microinstability Driven Turbulence in the Madison Symmetric Torus }, US Transport Task Force Workshop, San Antonio, TX - April 2014
\item Poster, {\it Gyrokinetic Characterization of PPCD Plasmas}, APS Division of Plasma Physics Annual Meeting, Denver, CO - November 2013
\item Poster, {\it Gyrokinetic Microinstability and Turbulence Studies in the RFP}, IEA-RFP Workshop, Padova, Italy - September 2013
\item Invited Talk, {\it Gyrokinetic simulations in the RFP}, US Transport Task Force Workshop, Santa Rosa, CA - April 2013
\item Poster, {\it Microtearing Mode Fluctuations in Reversed Field Pinch Plasmas}, International Atomic Energy Agency Fusion Energy Conference, San Diego, CA - October 2012
\item Poster, {\it Microtearing Simulations in the Madison Symmetric Torus}, APS Division of Plasma Physics Annual Meeting, Providence, RI - October 2012
\item Poster, {\it Gyrokinetic modeling of microinstabilities in the reversed field pinch}, US Transport Task Force Workshop, Annapolis, MD - April 2012
\item Poster, {\it Gyrokinetic Studies of Microtearing Modes in the Reversed Field Pinch}, APS Division of Plasma Physics Annual Meeting, Salt Lake City, UT - November 2011, Abstract GP9.00038
\item Talk, {\it Gyrokinetic Simulations and Microinstabilities in the RFP}, IEA-RFP Workshop, Madison, Wisconsin - October 2011
\item Poster, {\it Evidence of a mid-mantle discontinuity beneath South America}, American Geophysical Union - Fall Meeting, San Francisco - 2006, abstract S53A-1303
\end{itemize}

\section*{Outreach}

\begin{itemize}
\item Talk, {\it Plasmas of the Universe}, Madison East High School Math Week, Madison, WI - May 2014
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
%    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}



\end{document}
